A non-intrusive reduced basis method using artificial neural networks

### 2017-09-11 report/article.tex
First draft sent to Jan on 09/06/17.

		As detailed in the previous section, the finite element discretization of the $\bg{\mu}$-dependent nonlinear differential problem \eqref{eq:pde-weak-reference}, combined with Newton's method, entails the assembly and resolution of (possibly) many linear systems of the form \eqref{eq:galerkin-linear-system}, whose dimension is directly related to $(i)$ the size of the underlying grid and $(ii)$ the order of the polynomial FE spaces adopted. Since the accuracy of the resulting discretization heavily relies on these two factors, a direct numerical approximation of the full-order model implies severe computational costs. Therefore, even resorting to high-performance parallel workstations, this approach is hardly affordable in \emph{many-query} and \emph{real-time} contexts. %, where one is interested in a fast and reliable prediction of an \emph{output of interest}, i.e, a functional of the field variable $u(\bg{\mu})$, for many instances of $\bg{\mu} \in \mathcal{P}$ \cite{Dep08}. 
		This motivates the broad use of \emph{reduced-order} models, across several inter-disciplinary areas, e.g., parameter estimation, optimal control, shape optimization and uncertainty quantification \cite{HSR16, QMN15}.

		\iffalse
		To derive a standard projection-based reduced basis method, we introduce the notion of \emph{solution manifold} $\mathcal{M}$, defined as
		\begin{equation*}
			\mathcal{M} = \big\lbrace u(\bg{\mu}) ~ : ~ \bg{\mu} \in \mathcal{P} \big\rbrace \subset V \, .
		\end{equation*}
		Similarly, its discrete counterpart $\mathcal{M}_h$ is given by
		\begin{equation*}
			\mathcal{M}_h = \big\lbrace u_h(\bg{\mu}) ~ : ~ \bg{\mu} \in \mathcal{P} \big\rbrace \subset V_h \, .
		\end{equation*}
		For any $\bg{\mu} \in \mathcal{P}$, we assume that the FE solution $u_h(\bg{\mu})$ can be lead as close as desired (in the $V$-norm) to the corresponding continuous solution $u_h(\bg{\mu})$ (either by refining the computational mesh or by increasing the order of the FE space), so that $\mathcal{M}_h$ provides a good approximation of $\mathcal{M}$. Hence, in the following we refer to $u_h(\bg{\mu})$ as the \emph{truth} solution.
		\fi

>>>>

		As detailed in the previous section, the finite element discretization of the $\bg{\mu}$-dependent nonlinear differential problem \eqref{eq:pde-weak-reference}, combined with Newton's method, entails the assembly and resolution of (possibly) many linear systems of the form \eqref{eq:galerkin-linear-system}, whose dimension is directly related to $(i)$ the size of the underlying grid and $(ii)$ the order of the polynomial FE spaces adopted. Since the accuracy of the resulting discretization heavily relies on these two factors, a direct numerical approximation of the full-order model implies severe computational costs. Therefore, even resorting to high-performance parallel workstations, this approach is hardly affordable in \emph{many-query} and \emph{real-time} contexts, where one is interested in a fast and reliable prediction of an \emph{output of interest}, i.e, a functional of the field variable $u(\bg{\mu})$, for many instances of $\bg{\mu} \in \mathcal{P}$ \cite{Dep08}. This motivates the broad use of \emph{reduced-order} models, across several inter-disciplinary areas, e.g., parameter estimation, optimal control, shape optimization and uncertainty quantification \cite{HSR16, QMN15}.

		To derive a standard projection-based reduced basis method, we introduce the notion of \emph{solution manifold} $\mathcal{M}$, defined as
		\begin{equation*}
			\mathcal{M} = \big\lbrace u(\bg{\mu}) ~ : ~ \bg{\mu} \in \mathcal{P} \big\rbrace \subset V \, .
		\end{equation*}
		Similarly, its discrete counterpart $\mathcal{M}_h$ is given by
		\begin{equation*}
			\mathcal{M}_h = \big\lbrace u_h(\bg{\mu}) ~ : ~ \bg{\mu} \in \mathcal{P} \big\rbrace \subset V_h \, .
		\end{equation*}
		For any $\bg{\mu} \in \mathcal{P}$, we assume that the FE solution $u_h(\bg{\mu})$ can be lead as close as desired (in the $V$-norm) to the corresponding continuous solution $u_h(\bg{\mu})$ (either by refining the computational mesh or by increasing the order of the FE space), so that $\mathcal{M}_h$ provides a good approximation of $\mathcal{M}$. Hence, in the following we refer to $u_h(\bg{\mu})$ as the \emph{truth} solution.
